---
title: "Lightning Talks Handout"
author: "R-Ladies Sydney"
date: "20/06/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(kableExtra)
library(tibble)
```

```{r, echo=FALSE}
# possible choices to include in the bingo
choices <- c(
  "Grew up in Sydney",
  "Enjoys cooking",
  "Works in finance",
  "Commutes to work on a bike",
  "Has a (mini) library of stats textbooks",
  "Knows C++",
  "Remembers floppy disks",
  "Lived in Boston for a time",
  "Has needed to let a data analysis run for 24+ hours",
  "Teaches statistics",
  "Has met Hadley Wickham",
  "Has written their own R package",
  "Is an academic",
  "Loves cheese",
  "Has a Twitter account",
  "Does not have a Facebook account",
  "Checks Twitter more frequently than email",
  "Knows how to tweet from within R",
  "Has used a package you’ve never heard of",
  "Has 3 siblings",
  "Likes to run",
  "Grew up on a farm",
  "Has 3+ data analysis apps on their computer",
  "Does yoga",
  "Is a member of Datacamp",
  "Is a PhD student",
  "Prefers Python to R",
  "Taught themself to code",
  "Is new to using R",
  "Has used a library card catalog",
  "Can knit (with needles and wool)",
  "Prefers read.csv to read_csv",
  "Has *opinions* about <- versus =",
  "Actually likes regular expressions",
  "Has at least one laptop hex sticker",
  "Has kids",
  "Can explain why Snapchat exists ",
  "Grew up in a small town",
  "Can play an unusual instrument",
  "Has run an experiment that didn’t work",
  "Kept their New Years resolution",
  "Has gone scuba or sky diving",
  "Has done the Harbour bridge climb",
  "Is a Mac user",
  "Uses a standing desk",
  "Enjoys gardening",
  "Holds a local public library card",
  "Has an interesting pet (not cat or dog)",
  "Likes to dance",
  "Prefers merlot to shiraz",
  "Favourite food is sushi",
  "Thinks Messina is overrated",
  "Has never been to Messina",
  "Has been to Uluru",
  "Is a member of other data science Meetups",
  "Is a member of Meetups not related to data science",
  "Uses a keep cup every day",
  "Owns reusable stainless steel straws",
  "Knows how to record but not write Excel macros",
  "Loves Andy Field",
  "Can see the Opera House from their office",
  "Can see the Harbour Bridge from their office",
  "Swims in the ocean more than once a week",
  "Wants to be a data scientist",
  "Wants to be an academic",
  "Is a data scientist",
  "Has never been to NZ",
  "Uses plastic free shampoo/conditioner",
  "Knows a Trump supporter",
  "Has a cat",
  "Has a dog",
  "Has a pet with a geeky name",
  "Loves Karaoke",
  "Doesn’t own a car",
  "Plays a musical instrument",
  "Walks 10000 steps every day",
  "Has been to another RLadies chapter event",
  "Is R-Curious",
  "Prefers a flat white to a long black",
  "Prefers chardonnay to sav. blanc"
)

# information for live tweeting
talks <- tibble(
  name = c(
    "Jessica Lee",
    "Emi Tanaka",
    "Wendy Wong",
    "Sarah Romanes",
    "Zoe Meers",
    "Lovisa Lannesand",
    "Kate Dodds",
    "Charles Gray"
  ),
  twitter_handle = c(
    " ",
    "@statsgen",
    "@abc_wendsss",
    "@sarah_romanes",
    "@zoe_meers",
    " ",
    "@kate_munnik",
    "@cantabile"
  ),
  talk_title = c(
    "Why I R?",
    "Making a Shiny interactive web application using R",
    "Transitioning from financial planning to data science",
    "My long journey learning R - then and now",
    "ggparliament: Parliament plots in the tidyverse",
    "From Excel to R in the world of finance",
    "Learning the lingo - An R newbie’s perspective",
    "My experience at runconf18"
  )
)

nrow <- 8
ncol <- 2

# latex package loading needs to be done explicitly
# when we're calling rmarkdown::render from big_doc.R
usepackage_latex("booktabs")
usepackage_latex("longtable")
usepackage_latex("array")
usepackage_latex("multirow")
usepackage_latex("xcolor", options="table")
usepackage_latex("wrapfig")
usepackage_latex("float")
usepackage_latex("colortbl")
usepackage_latex("pdflscape")
usepackage_latex("tabu")
usepackage_latex("threeparttable")
usepackage_latex("threeparttablex")
usepackage_latex("ulem", options = "normalem")
usepackage_latex("makecell")

# create and style a kable for bingo
bingo_card <- choices %>% 
  sample(size = nrow * ncol) %>%
  matrix(nrow = nrow, ncol = ncol) %>% 
  kable(format = "latex", booktabs=TRUE) %>% 
  kable_styling(latex_options = "striped")  

# ditto for the talks
talk_table <- talks %>% 
  kable(format = "latex", booktabs=TRUE) %>% 
  kable_styling(latex_options = "striped")  
```

## Get to know the Sydney R-Ladies!

It's a launch event, so why not get to know your fellow R-Ladies? As an ice-breaker, every handout has a "bingo" card. See if you can find someone who...

```{r,echo=FALSE}
bingo_card
```

The bingo cards are randomised -- using R, naturally, because we are stats nerds! -- so everyone should have a slightly different list of things to find! 

## Want to live tweet about the talks?

```{r,echo=FALSE}
talk_table
```


- Don't forget to @ the speaker in the tweet :-)
- Include the #rladies hashtag. Adding @rladiessydney optional
- Include a picture! (speaker or slides)
- Speaker info is on the blog: http://rladiessydney.org/posts/lightning-talks/

## R-Ladies Sydney info

- Website: http://rladiessydney.org/, Meetup:  http://meetup.com/rladies-sydney, Twitter: @rladiessydney, Email: sydney@rladies.org, GitHub: https://github.com/rladiessydney
- Jen Richmond: @JenRichmondPhD, Steph De Silva: @StephdeSilva, Lisa Williams: @williamslisaphd, Dani Navarro: @djnavarro




