---
title: "Lightning Talks Handout"
author: "R-Ladies Sydney"
date: "20/06/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(kableExtra)
library(tibble)
```

```{r, echo=FALSE}
# possible choices to include in the bingo
choices <- c(
  "Grew up in Sydney",
  "Enjoys cooking",
  "Works in finance",
  "Commutes to work on a bike",
  "Has a (mini) library of stats textbooks",
  "Knows C++",
  "Remembers floppy disks",
  "Lived in Boston for a time",
  "Has needed to let a data analysis run for 24+ hours",
  "Teaches statistics",
  "Has met Hadley Wickham",
  "Has written their own R package",
  "Is an academic",
  "Loves cheese",
  "Has a Twitter account",
  "Has used a package you’ve never heard of",
  "Has 3 siblings",
  "Likes to run",
  "Grew up on a farm",
  "Has 3+ data analysis apps on their computer",
  "Does yoga",
  "Is a member of Datacamp",
  "Is a PhD student",
  "Prefers Python to R",
  "Taught themself to code",
  "Is new to using R",
  "Has used a library card catalog",
  "Can knit",
  "Has *opinions* about <- versus =",
  "Knows regular expressions",
  "Has at least one laptop hex sticker",
  "Has kids",
  "Can explain why Snapchat exists ",
  "Grew up in a small town",
  "Can play an unusual instrument",
  "Has run an experiment that didn’t work",
  "Kept their New Years resolution",
  "Has gone scuba or sky diving",
  "Has done the Harbour bridge climb",
  "Knows an RStudio trick you don't"
)

# information for live tweeting
talks <- tibble(
  name = c(
    "Jessica Lee",
    "Emi Tanaka",
    "Wendy Wong",
    "Sarah Romanes",
    "Zoe Meers",
    "Lovisa Lannesand",
    "Kate Dodds",
    "Charles Gray"
  ),
  twitter_handle = c(
    " ",
    "@statsgen",
    "@abc_wendsss",
    "@sarah_romanes",
    "@zoe_meers",
    " ",
    "@kate_munnik",
    "@cantabile"
  ),
  talk_title = c(
    "Why I R?",
    "Making a Shiny interactive web application using R",
    "Transitioning from financial planning to data science",
    "My long journey learning R - then and now",
    "ggparliament: Parliament plots in the tidyverse",
    "From Excel to R in the world of finance",
    "Learning the lingo - An R newbie’s perspective",
    "My experience at runconf18"
  )
)

nrow <- 8
ncol <- 2

# latex package loading needs to be done explicitly
# when we're calling rmarkdown::render from big_doc.R
usepackage_latex("booktabs")
usepackage_latex("longtable")
usepackage_latex("array")
usepackage_latex("multirow")
usepackage_latex("xcolor", options="table")
usepackage_latex("wrapfig")
usepackage_latex("float")
usepackage_latex("colortbl")
usepackage_latex("pdflscape")
usepackage_latex("tabu")
usepackage_latex("threeparttable")
usepackage_latex("threeparttablex")
usepackage_latex("ulem", options = "normalem")
usepackage_latex("makecell")

# create and style a kable for bingo
bingo_card <- choices %>% 
  sample(size = nrow * ncol) %>%
  matrix(nrow = nrow, ncol = ncol) %>% 
  kable(format = "latex", booktabs=TRUE) %>% 
  kable_styling(latex_options = "striped")  

# ditto for the talks
talk_table <- talks %>% 
  kable(format = "latex", booktabs=TRUE) %>% 
  kable_styling(latex_options = "striped")  
```

## Get to know the Sydney R-Ladies!

It's a launch event, so why not get to know your fellow R-Ladies? As an ice-breaker, every handout has a "bingo" card. See if you can find someone who...

```{r,echo=FALSE}
bingo_card
```

The bingo cards are randomised -- using R, naturally, because we are stats nerds! -- so everyone should have a slightly different list of things to find! 

## Want to live tweet about the talks?

```{r,echo=FALSE}
talk_table
```


- Don't forget to @ the speaker in the tweet :-)
- Include the #rladies hashtag. Adding @rladiessydney optional
- Include a picture! (speaker or slides)
- Speaker info is on the blog: http://rladiessydney.org/posts/lightning-talks/

## R-Ladies Sydney info

- Website: http://rladiessydney.org/, Meetup:  http://meetup.com/rladies-sydney, Twitter: @rladiessydney, Email: sydney@rladies.org, GitHub: https://github.com/rladiessydney
- Jen Richmond: @JenRichmondPhD, Steph De Silva: @StephdeSilva, Lisa Williams: @williamslisaphd, Dani Navarro: @djnavarro



  
